A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 application_to_path_tracing.tex
Plop
Correction

\begin{figure}[tbhp]
\begin{center}
\includegraphics[scale=0.17]{images/four_scenes_for_dgci.png}
\caption{\label{fig:results}Same scene using the classical path tracing (image $a$) or our method (image $b$). Images $c$ and $d$ are both details of respectivelly images $a$ and $b$ }
\end{center}
\end{figure}

>>>>

\begin{figure}[tbhp]
\begin{center}
\includegraphics[scale=0.17]{images/four_scenes_for_dgci.png}
\caption{\label{fig:results}Same scene rendered using the classical path tracing (image $a$) or our method (image $b$). Images $c$ and $d$ are both details of respectively images $a$ and $b$ }
\end{center}
\end{figure}
